Results

### 2025-07-25 notebooks/000_data.qmd
feat: add alpha

```{julia}
using Dates
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using SPEDAS: tplot
using GLMakie
```

@@

>>>>

```{julia}
using Dates
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using SPEDAS: tplot, set_meta
using GLMakie
```

@@

the helium-to-proton abundance ratio ($A_{He} = N_α/N_p × 100\%$, where $N_α$ and $N_p$ are the number densities of helium particles and protons, respectively)

```{julia}
tmin = DateTime("2021-01-15")
n_p = PSP.n_spi(tmin, tmin + Day(1))
n_α = PSP.n_alpha(tmin, tmin + Day(1))

A_He = set_meta(n_α ./ n_p .* 100; ylabel="A_He", units="%", scale=identity)

let tmin = DateTime("2021-01-15")
    tvars = (
        PSP.n_spi,
        PSP.n_alpha,
        A_He
    )
    tplot(tvars, tmin, tmin + Day(1))
end
```
